Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-01 manuscript/manuscript.tex
Fixed typos

It's well known that the GLQ method becomes less accurate when the computation point is closer to the tesseroid \citep{Ku1977} or for smaller GLQ order. 
Although the model developed by \citet{Uieda2016} uses a second order GLQ, it ensures the accuracy implementing a modified version of the adaptative discretization of \citet{Li2011}.
It consist in splitting the tesseroid into smaller ones when a certain distance-size ratio ($D$) is greater than a predefined value that controls the precision of the computation.  \citet{Uieda2016} have also objectively obtained standard values of $D$ for gravity potential, gradients and tensor components comparing the fields generated by a spherical shell, which constitutes a special case of the volume integrals that has analytical solution \citep{LaFehr1991, Mikuska2006, Grombein2013}\todo{citar mas??}.
The modifications made by \citet{Uieda2016} to the original adaptative discretization method \citep{Li2011} consist in:
(1) a faster calculation of the distance from the computation point to the tesseroid and 
(2) the application of a stack based algorithm that speeds up the computation and gives more control over the recursion step.

@@

The spherical prisms known as tesseroids are mass elements defined in a geocentric spherical coordinate system bounded by a pair of parallels, a pair of  meridians, and two concentric spherical surfaces.
We define an external computation point $P(r, \phi, \lambda)$ where the gravity fields generated by the tesseroid are going to be calculated with respect to the local north oriented cartesian coordinate system located at $P$.
In the special case of homogeneous density, the gravity potential, gradient and Marussi tensor components can be calculated through the integrals obtained by \citet{Grombein2013} \citep[see also][]{Uieda2016}.

@@

For example, if we use a second order GLQ, the roots of the $P_2(x)$ Legendre polynomial and its corresponding weights are $x_i = \pm 0.577350269$ and $W_i = 1$, respectivetly.

@@

\todo{speed comparission between homogeneous and variable density}

@@

Instead of increasing the GLQ orders, what leads to a more time consuming computation, adaptative discreatization algorithms have been applied in previous works \citep{Li2011, Uieda2016}.
They basically consist in dividing the tesseroid based on a ratio between its size and the distance between its geometric centre and the computation point.

In order to make the computation more efficient, we use only second order GLQ for each integration, and we ensure the accuracy of the method through the application of the modified adaptative discretization algorithm developed by \citet{Uieda2016}.

@@

\noindent where $i \in \{\lambda, \phi, r\}$, $d$ is the distance between the geometric centre of the tesseroid and the computation point and $D$ is a predefined value called distance-size ratio.
If the inequality \ref{eq:distance-size-ratio} is not held for any spherical coordinate, then the tesseroid must be divided by half in that direction.

>>>>

It's well known that the GLQ method becomes less accurate when the computation point is closer to the tesseroid \citep{Ku1977} or for smaller GLQ order. 
Although the model developed by \citet{Uieda2016} uses a second order GLQ, it ensures the accuracy implementing a modified version of the adaptive discretization of \citet{Li2011}.
It consist in splitting the tesseroid into smaller ones when a certain distance-size ratio ($D$) is greater than a predefined value that controls the precision of the computation.  \citet{Uieda2016} have also objectively obtained standard values of $D$ for gravity potential, gradients and tensor components comparing the fields generated by a spherical shell, which constitutes a special case of the volume integrals that has analytical solution \citep{LaFehr1991, Mikuska2006, Grombein2013}\todo{citar mas??}.
The modifications made by \citet{Uieda2016} to the original adaptive discretization method \citep{Li2011} consist in:
(1) a faster calculation of the distance from the computation point to the tesseroid and 
(2) the application of a stack based algorithm that speeds up the computation and gives more control over the recursion step.

@@

The spherical prisms known as tesseroids are mass elements defined in a geocentric spherical coordinate system bounded by a pair of parallels, a pair of  meridians, and two concentric spherical surfaces.
We define an external computation point $P(r, \phi, \lambda)$ where the gravity fields generated by the tesseroid are going to be calculated with respect to the local north oriented Cartesian coordinate system located at $P$.
In the special case of homogeneous density, the gravity potential, gradient and Marussi tensor components can be calculated through the integrals obtained by \citet{Grombein2013} \citep[see also][]{Uieda2016}.

@@

For example, if we use a second order GLQ, the roots of the $P_2(x)$ Legendre polynomial and its corresponding weights are $x_i = \pm 0.577350269$ and $W_i = 1$, respectively.

@@

\todo{speed comparison between homogeneous and variable density}

@@

Instead of increasing the GLQ orders, what leads to a more time consuming computation, adaptive discretization algorithms have been applied in previous works \citep{Li2011, Uieda2016}.
They basically consist in dividing the tesseroid based on a ratio between its size and the distance between its geometric centre and the computation point.

In order to make the computation more efficient, we use only second order GLQ for each integration, and we ensure the accuracy of the method through the application of the modified adaptive discretization algorithm developed by \citet{Uieda2016}.

@@

\noindent where $i \in \{\lambda, \phi, r\}$, $d$ is the distance between the geometric centre of the tesseroid and the computation point and $D$ is a predefined value called distance-size ratio.
If the inequality \ref{eq:distance-size-ratio} is not held for any spherical coordinate, then the tesseroid must be divided by half in that direction.
A more complete description of the modified adaptive discretization algorithm can be found in \citet{Uieda2016}.
